%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Primordial Machine's Vectors Library
% Copyright (C) 2017-2019 Michael Heilmann
%
% This software is provided 'as-is', without any express or implied warranty.
% In no event will the authors be held liable for any damages arising from the
% use of this software.
%
% Permission is granted to anyone to use this software for any purpose,
% including commercial applications, and to alter it and redistribute it
% freely, subject to the following restrictions:
%
% 1. The origin of this software must not be misrepresented;
%    you must not claim that you wrote the original software.
%    If you use this software in a product, an acknowledgment
%    in the product documentation would be appreciated but is not required.
%
% 2. Altered source versions must be plainly marked as such,
%    and must not be misrepresented as being the original software.
%
% 3. This notice may not be removed or altered from any source distribution.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[oneside]{book}

\input{common}

\SetOrganization{Primordial Machine's}
\SetLibraryName{Vectors Library}

\SetLibraryIncludeFileName{include.hpp}
\SetLibraryIncludesDirectoryPath{primordialmachine/math-vectors/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/includes}

\SetLibraryIncludeDirectiveFilePath{primordialmachine/math/vectors/include.hpp}

\SetLibraryStaticLibrariesDirectoryPath{primordialmachine/math-vectors/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/libraries}
\SetLibraryStaticLibraryFileName{math-vectors.lib}

\SetLibraryVersion{v1.0}
\SetLibraryRepository{https://github.com/primordialmachine/math-vectors}
\SetAuthor{Michael Heilmann}
\SetEmail{michaelheilmann@primordialmachine.com}

\SetDocumentType{User Manual}

\begin{document}

\frontmatter

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
\addtocontents{toc}{\protect\thispagestyle{empty}}
\pagenumbering{gobble}

\mainmatter

\chapter{Synopsis}
C++ 17 library providing floating point vectors over $n$ dimensions.
The library is made available publicly on
\href{\GetLibraryRepository}{Github}
under the
\href{\GetLibraryRepository/blob/master/LICENSE}{MIT License}.

\chapter{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.

\chapter{Introductory example}
\textit{\color{orange}This library does not provide any examples yet.}
%Examples are located in the \href{\GetLibraryRepository/blob/master/examples}{examples} directory.

\input{building_visual_studio_2017}

\chapter{Library Interface Documentation}

\section{\texttt{namespace primordialmachine}}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below.

\input{functors}

\section{\texttt{vector\_traits} (struct)}
\begin{verbatim}
template<typename ELEMENT_TYPE, typename NUMBER_OF_ELEMENTS>
struct vector_traits;
\end{verbatim}

\section{\texttt{is\_vector} (struct)}
\texttt{
template \textlangle typename TYPE, typename ENABLED = void\textrangle\newline
struct is\_vector {\newline
  static bool const value = false;\newline
};}

\noindent{}This template defines a compile-time boolean constant \texttt{value}
which can be used to determine whether a type \texttt{TYPE} is a valid vector type.
This library provides specialization for its \texttt{vector} template specializations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\texttt{vector} (struct)}
\begin{verbatim}
template<typename TRAITS, typename ENABLED = void>
struct vector;
\end{verbatim}
\noindent{}This library provides specializations where \texttt{TRAITS} is a \texttt{vector\_traits}
specialization with the following properties:
\begin{enumerate}
	\item \texttt{ELEMENT\_TYPE} is a type \texttt{TYPE} for which \texttt{is\_scalar\textlangle TYPE \textrangle::value} is \texttt{true}.
	\item \texttt{NUMBER\_OF\_ELEMENTS} is any number between 0 and \texttt{std::numeric\_limits\textlangle size\_t\textrangle\::max()}.
\end{enumerate}



\subsection{Members}

\subsection{Non Members}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{operator+} (binary, vector vector)}
\begin{verbatim}
template<typename U, typename V>
typename binary_plus_functor<vector<U>, vector<V>>::result_type
operator+(const vector<U>& u, const vector<V>& v)
{ return binary_plus_functor<vector<U>, vector<V>>()(u, v); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle U\textrangle}
and \texttt{vector\textlangle V\textrangle} where
\begin{enumerate}
	\item \texttt{U::number\_of\_elements} is equal to \texttt{V::number\_of\_elements} and
	\item \texttt{U::element\_type} and \texttt{V::element\_type} are floating point types.
\end{enumerate}

\subsubsection{\texttt{operator+} (unary, vector)}
\begin{verbatim}
template<typename V>
typename unary_plus_functor<vector<V>>::result_type
operator+(const vector<V>& v)
{ return unary_plus_functor<vector<V>>()(v); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle V\textrangle}
where \texttt{V::element\_type} is a floating point type.

\subsubsection{\texttt{operator+=} (vector vector)}
\begin{verbatim}
template<typename U, typename V>
auto
operator-=(vector<U>& u, const vector<V>& v)
{
   u = u + v;
   return u;
}
\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{operator-} (binary, vector vector)}
\begin{verbatim}
template<typename U, typename V>
typename binary_minus_functor<vector<U>, vector<V>>::result_type
operator-(const vector<U>& u, const vector<V>& v)
{ return binary_minus_functor<vector<U>, vector<V>>()(u, v); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle U\textrangle}
and \texttt{vector\textlangle V\textrangle} where
\begin{enumerate}
	\item \texttt{U::number\_of\_elements} is equal to \texttt{V::number\_of\_elements} and
	\item \texttt{U::element\_type} and \texttt{V::element\_type} are floating point types.
\end{enumerate}

\subsubsection{\texttt{operator-} (unary, vector)}
\begin{verbatim}
template<typename V>
typename unary_minus_functor<vector<V>>::result_type
operator-(const vector<V>& v)
{ return unary_minus_functor<vector<V>>()(v); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle V\textrangle}
where \texttt{V::element\_type} is a floating point type.

\subsubsection{\texttt{operator-=} (vector vector)}
\begin{verbatim}
template<typename U, typename V>
auto
operator-=(vector<U>& u, const vector<V>& v)
{
   u = u - v;
   return u;
}
\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{operator*} (binary, vector vector)}
Computes the sum of two vectors.
A possible implementation is
\begin{verbatim}
template<typename U, typename V>
typename binary_star_functor<vector<U>, vector<V>>::result_type
operator*(const vector<U>& u, const vector<V>& v)
{ return binary_star_functor<vector<U>, vector<V>>()(u, v); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle U\textrangle}
and \texttt{vector\textlangle V\textrangle} where
\begin{enumerate}
	\item \texttt{U::number\_of\_elements} is equal to \texttt{V::number\_of\_elements} and
	\item \texttt{U::element\_type} and \texttt{V::element\_type} are floating point types.
\end{enumerate}

\subsubsection{\texttt{operator*=} (binary, vector vector)}
\begin{verbatim}
template<typename U, typename V>
auto
operator*=(vector<U>& u, const vector<V>& v)
{
   u = u * v;
   return u;
}
\end{verbatim}

\subsubsection{\texttt{operator*} (binary, vector scalar)}
\begin{verbatim}
template<typename V, typename S>
typename binary_star_functor<vector<V>, S>::result_type
operator*(const vector<V>& v, S s)
{ return binary_star_functor<vector<V>, S>()(v, s); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle V\textrangle}
and \texttt{S} where    \texttt{V::element\_type} and \texttt{S} are floating point
types.

\subsubsection{\texttt{operator*=} (binary, vector scalar)}
\begin{verbatim}
template<typename V, typename S>
auto
operator*=(vector<V>& v, S s)
{
   v = v * s;
   return v;
}
\end{verbatim}

\subsubsection{\texttt{operator*} (binary, scalar vector)}
\begin{verbatim}
template<typename S, typename V>
auto
operator*(S s, vector<V>& v)
{
   return s * v;
}
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{operator/} (binary, vector scalar)}
\begin{verbatim}
template<typename V, typename S>
typename binary_slash_functor<vector<V>, S>::result_type
operator/(const vector<V>& v, S s)
{ return binary_slash_functor<vector<V>, S>()(v, s); }
\end{verbatim}
This library provides a specializations for \texttt{vector\textlangle V\textrangle}
and \texttt{S} where    \texttt{V::element\_type} and \texttt{S} are floating point
types.

\subsubsection{\texttt{operator/=} (binary, vector scalar)}
\begin{verbatim}
template<typename V, typename S>
auto
operator/=(vector<V>& v, S s)
{
   v = v / s;
   return v;
}
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{dot\_product\_functor} (struct)}
a \textit{BinaryFunctorBase} computing the dot product of two vectors.
A possible implementation is given by
\begin{verbatim}
template<typename LEFT_OPERAND, typename RIGHT_OPERAND, typename ENABLED = void>
struct dot_product_functor;
\end{verbatim}

This library provides \textit{BinaryFunctor} specializations of this \textit{BinaryFunctorBase}
where \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} are specializations of \texttt{vector}
with the same number of elements $N$. The result type \texttt{result\_type}          is\newline
\texttt{std::common\_type\_t\textlangle LEFT\_OPERAND\_TRAITS::element\_type, RIGHT\_OPERAND\_TRAITS::element\_type\textrangle}\newline
 where \texttt{LEFT\_OPERAND\_TRAITS} and \texttt{RIGHT\_OPERAND\_TRAITS} are the traits of these specializations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{cross\_product\_functor} (struct)}
A \textit{BinaryFunctorBase} computing the cross product of two vectors.
A possible implementation is given by
\begin{verbatim}
template<typename LEFT_OPERAND, typename RIGHT_OPERAND, typename ENABLED = void>
struct cross_product_functor;
\end{verbatim}

This library provides \textit{BinaryFunctor} specializations of this \textit{BinaryFunctorBase}
where \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} are specializations of \texttt{vector} with   the
same number of elements $3$. The result type \texttt{result\_type} is  \texttt{vector\textlangle RESULT\_TRAITS\textrangle}
where\newline
\texttt{
RESULT\_TRAITS:=vector\_traits\textlangle std::common\_type\_t\textlangle{}LEFT\_OPERAND\_TRAITS::element\_type,\newline%
\hphantom{RESULT\_TRAITS:=vector\_traits\textlangle std::common\_type\_t\textlangle}RIGHT\_OPERAND\_TRAITS::element\_type\textrangle,\newline%
\hphantom{RESULT\_TRAITS:=vector\_traits\textlangle}3\textrangle}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{square\_euclidean\_norm\_functor} (struct)}
A \textit{UnaryFunctorBase} computing the squared Euclidean norm of a vector.
A possible implementation is given by
\begin{verbatim}
template<typename OPERAND, typename ENABLED = void>
struct square_euclidean_norm_functor;
\end{verbatim}

This library provides \textit{UnaryFunctor} specializations of this \textit{UnaryFunctorBase}
where \texttt{OPERAND} is specializations of \texttt{vector}. The result type        \texttt{
result\_type} is \texttt{OPERAND\_TRAITS::element\_type\textrangle}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{euclidean\_norm\_functor} (struct)}
An \textit{UnaryFunctorBase} computing the Euclidean norm of a vector.
A possible implementation is given by
\begin{verbatim}
template<typename OPERAND, typename ENABLED = void>
struct euclidean_norm_functor;
\end{verbatim}

This library provides \textit{UnaryFunctor} specializations of this \textit{UnaryFunctorBase}
where \texttt{OPERAND} is specializations of \texttt{vector}. The result type        \texttt{
result\_type} is \texttt{OPERAND\_TRAITS::element\_type}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{normalize\_functor} (struct)}
A \textit{UnaryFunctorBase} computing the normalized vector of a vector.
A possible implementation is given by
\begin{verbatim}
template<typename OPERAND, typename NORM, typename ENABLED = void>
struct normalize_functor;
\end{verbatim}
\texttt{NORM} is an additional template argument denoting the type of norm functor.\newline

This library provides \textit{UnaryFunctor} specializations of this \textit{UnaryFunctorBase} where
\texttt{OPERAND} is specializations of \texttt{vector}. The result type \texttt{result\_type}    is
\texttt{vector\textlangle RESULT\_TRAITS\textrangle} where \texttt{RESULT\_TRAITS}               is
\texttt{OPERAND\_TRAITS}.\newline

The \texttt{operator()} has a third parameter  \texttt{norm} which defaults to
\texttt{euclidean\_norm\textlangle vector\textlangle RESULT\_TRAITS\textrangle
\textrangle} through which any other norm can be passed.\newline

\textit{\textcolor{orange}{The \textit{ParameterizedBinaryFunctor(Base)} concepts - like
\texttt{normalize\_functor}       - subsumes the \textit{BinaryFunctor(Base)}  concepts.
Add the \textit{ParameterizedBinaryFunctor(Base) concepts.}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\texttt{are\_orthogonal\_functor} (struct)}
A \textit{BinaryFunctorBase} computing if two vectors are orthogonal.
A possible implementation is given by
\begin{verbatim}
template<typename OPERAND, typename NORM, typename EQUAL_TO, typename ENABLED = void>
struct are_orthogonal_functor;
\end{verbatim}
\texttt{EQUAL\_TO} is an additional template argument denoting the type of an equal to functor.\newline

This library provides \textit{UnaryFunctor} specializations of this \textit{UnaryFunctorBase}
where \texttt{OPERAND} is specializations of \texttt{vector}. The result type        \texttt{
result\_type} is \texttt{bool}.\newline

The \texttt{operator()} has a third parameter \texttt{norm}   which accepts an
\texttt{equal\_to\_functor\textlangle SCALAR, SCALAR\textrangle}         where
\texttt{SCALAR} is \texttt{std::common\_type\_t                    \textlangle
LEFT\_OPERAND\_TRAITS::element\_type,    RIGHT\_OPERAND\_TRAITS::element\_type
\textrangle}.\newline

\textit{\textcolor{orange}{The \textit{ParameterizedBinaryFunctor(Base)} concepts - like
\texttt{are\_orthogonal\_functor} - subsumes the \textit{BinaryFunctor(Base)}  concepts.
Add the \textit{ParameterizedBinaryFunctor(Base) concepts.}}}

\subsubsection{\texttt{are\_orthogonal} (function)}
A \textit{BinaryFunction} computing if two vector

\end{document}
